---
title: "Milestone 3"
author: "Pieter Quinton"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(dplyr)
```

```{r}
zillow_data <- read.csv("Metro_Zhvi_SingleFamilyResidence.csv")
top_tier <- read.csv("Metro_Zhvi_TopTier.csv")
bottom_tier <- read.csv("Metro_Zhvi_BottomTier.csv")
```

##Overview of Data  

As of right now, my data comes from Zillow. More specifically, it comes from the Zillow Research Housing Data page (https://www.zillow.com/research/data/). I have downloaded three data sets which show the median housing prices across over 800 of the largest metropolitan areas in the country from 1996 to 2019 broken down by month. Of the three data sets, one is the median house price for all homes in the metro area. One is the median house price for just houses in the bottom tier and the last one is for just houses in the top tier. I intend to supplement these sets with additional data from the census bureau on population and housing construction over a similar time period. 

##Plan of Action  

My goal is to, in part, illustrate the trend in housing prices across the United States over the past couple of decades. My aim is to create an interactive animated plot which shows the changing median housing prices over time and allows the user to select the cities they want to appear on the plot. I would also like to create an interactive map of the United States which allows you to see the median house price of a metropolitan area by hovering over the city. 
